%-------------------------------------------------------------------------------
% RLResume
%-------------------------------------------------------------------------------
\documentclass{RLResume}

\usepackage[hscale=0.85,vscale=0.9]{geometry}

% personal data
\name{Riley Labrecque}
\RequirePackage{PrivateData}
\homepage{rileylabrecque.com}
%\social[linkedin]{rileylabrecque}
%\social[twitter]{rileylabrecque}
%\social[github]{rlabrecque}

\begin{document}

\makecvtitle

\section{Experience}
\cventry{Apr 2019 --\newline Present}{Lead Systems Engineer}{First Strike Games}{
\begin{itemize}
    \item Designing and implementing online services in Unreal Engine 4, from the backend to UI.
    \item Debugging, optimization, build engineering, and tooling on Windows, Linux, and consoles.
    \item Maintaining communication with our technical partners.
    \item Mentoring, leading, documenting features and practices, and putting out fires.
\end{itemize}
}

\cventry{Sep 2017 --\newline Mar 2019}{Client Network Engineer (Remote)}{First Strike Games}{}

\cventry{Jul 2016 --\newline Jul 2017}{Technical Writer (Remote Contract)}{Valve Corporation}{
\begin{itemize}
    \item Writing documentation for Steam partners.
    \begin{itemize}
        \item Rewrote the entire Steam API documentation for programmers.
    \end{itemize}
    \item Created various tools to assist with the documentation efforts.
    \begin{itemize}
        \item Auto generated API documentation pages which allowed us to make large sweeping changes quickly and easily and keep the documentation in sync with the code.
        \item Static analyzer that caught common errors before reaching customers and served as a  progress report.
    \end{itemize}
\end{itemize}
}

\cventry{Jun 2014 --\newline Jul 2016}{Freelance Software Engineer}{One Indirection Software}{
  \begin{itemize}
    \item Providing consulting and development services to indie game developers with a heavy focus on Unity.
    \item Worked directly with many great titles across a large range of studios, some of my favorites include:
    \begin{itemize}
        \item \textit{Autocraft} \& \textit{Modbox} by Alientrap Games
        \begin{itemize}
            \item Implemented the user-generated content sharing platform with the Steam Workshop.
            \item Performance optimization for VR.
        \end{itemize}
            \item \textit{AaaaaA! for the Awesome} \& \textit{Dyscourse} by Owlchemy Labs, LLC
        \begin{itemize}
            \item Implemented a number of value-added features including achievements and leaderboards.
            \item Porting from Windows to OSX and Linux and debugging.
        \end{itemize}
            \item \textit{Vertiginous Golf} by Kinelco
        \begin{itemize}
            \item Implemented Steam Leaderboards and designed an API to use them from Javascript.
        \end{itemize}
    \end{itemize}
  \end{itemize}
}

\cventry{Sep 2013 --\newline Mar 2014}{Software Engineer}
{Shorebound Studios}{
  \begin{itemize}
      \item I was handed complete control over the previously released game \textit{Spectraball}.
      \item Increased revenue by over 400\% month-over-month by identifying and implementing market strategies.
  \end{itemize}
}

\cventry{Jan 2012 --\newline Sep 2013}{Freelance Software Engineer}{}{
    \begin{itemize}
        \item Commissioned server plugins for \textit{Counter-Strike: Source} community game servers.
    \end{itemize}
}

\cventry{Jul 2007 --\newline Aug 2013}{Web Developer \& Game Designer}{Obsession Soft}{
    \begin{itemize}
        \item Helped turn \textit{Kreedz Climbing} into one of the largest Source engine mods ever by player count.
    \end{itemize}
}

\iffalse
    \cventry{Dec 2006 --\newline May 2007}{Newspaper and Flyer Carrier}{Saskatoon Sun}{
        \begin{itemize}
            \item Delivery of bi-weekly flyers and newspapers
        \end{itemize}
    }

    \cventry{May 2006 --\newline Sep 2014}{Pet Care and Home Attendant}{}{
        \begin{itemize}
            \item Dog sitting and dog walking in the neighborhood
            \item Mowing lawn, shoveling snow, and mail care in the neighborhood
        \end{itemize}
    }

    \cventry{Sep 2002 --\newline Aug 2003}{Newspaper Carrier}{Star Phoenix}{
        \begin{itemize}
            \item Daily early morning delivery and monthly collection for newspaper route
        \end{itemize}
    }

    \cventry{Sep 1999 --\newline Jun 2003}
    {Home-based Business "Riley's Reflections"}{}{
        \begin{itemize}
          \item Production and sales of candles.
          \item Development of business skills.
          \item Business trips to supplier in Edmonton, Alberta.
        \end{itemize}
    }
\fi

\section{Other}
\cventry{Aug 2014}{Conference Talk: Crash Course on Implementing Steamworks SDK}{Unity Unite 2014}{}
\cventry{Sep 2013 --\newline Present}{Project: Steamworks.NET}{}{
    \begin{itemize}
        \item Unity plugin to easily integrate with Valve's Steamworks SDK.
        \item Used by over 400 shipping Unity games and roughly 2/3 of all Unity games shipped on Steam, including:
        \begin{itemize}
            \item \textit{
            7 Days to Die,
            Distance,
            Dyscourse,
            Infinifactory,
            Job Simulator,
            Kerbal Space Program,
            Mushroom 11,
            Race The Sun,
            RimWorld,
            Robocraft,
            Slime Rancher,
            Stardew Valley,
            Terraria,
            The Elder Scrolls: Legends,
            The Long Dark,
            The Swapper,
            Unturned,
            Verdun,
            Windward,
            Yooka-Laylee
            }
        \end{itemize}
    \end{itemize}
    }

\section{Technical Experience}
\subsection{Proficient with}
\cvitem{Languages}{
    C,
    C++,
    C\#,
    Javascript,
    PHP,
    Python,
    Regex,
    SourcePawn,
    TypeScript
}
\cvitem{Technologies}{
    Docker,
    Git,
    Linux,
    Mobx,
    Node.js,
    Perforce,
    Protobuf,
    React,
    Unity,
    Unreal Engine 4,
    Valve Hammer Editor,
    Visual Studio,
    Webpack,
    Win32
}

\subsection{Have Experience with}
\cvitem{Languages}{
    Go,
    Java,
    HTML,
    Lua
}
\cvitem{Technologies}{
    Blender,
    Blizzard World Editors,
    DirectX,
    GCC,
    GDB,
    IDA Pro + Hex Rays,
    Kubernetes,
    LaTeX,
    Mercurial,
    MySQL,
    Photoshop,
    Qt,
    Subversion,
    WPF,
    XCode
}

\clearpage
\end{document}
